Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-18 bdcloud_paper/latex/paper.tex
Add customer-store distance data

First, we wanted to identify how close most customers live to a store since advertising to people who live or work too far away from a store is unlikely to be effective and will increase our costs. We analyzed the distribution of distances between customers' homes and their nearest stores.  We found that most customers tend to live within 10 miles of their closest store, suggesting that we should limit our advertising to a 10-mile radius around each our store.

\textcolor{red}{figure}

>>>>

First, we wanted to identify how close most customers live to a store since advertising to people who live or work too far away from a store is unlikely to be effective and will increase our costs. We analyzed the distribution of distances between customers' homes and their nearest stores.  We found that most customers tend to live within 15 miles of their closest store, suggesting that we should limit our advertising to a 15-mile radius around each our store.

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.5in]{figures/customer_store_distances.eps}
  \caption{Distributions of Distances of Customers to Closest Stores}
  \label{fig:cluster_analysis}
\end{figure}
